---
title: "920-My_First_Rmarkdown"
author: "Sérgio Pereira"
date: "2023-03-04"
output: pdf_document
---

## Setting up my Environment   
Loading the packages that i will need. In this case 'tidyverse' , 'palmerpenguins' and ggplot2

```{r Packages_Load, echo=FALSE}
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
head(penguins)
```

<br>

## Visualizations

Next, we will see two graphs that have conclusions about the Palmer Penguins and Hotel Bookings Databases.

But first, the table visualizations.

<br>

# Penguins

## Palmer Penguins Body Mass and Flipper Length

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point(aes(color=species))+
  labs(title="Palmer Penguins Body Mass and Flipper Length",subtitle = "By Gender and Sex",
       caption = "Dr. Gorman - 2007-2009")+
  annotate("text", x=222, y=4100, label="Gentoo males are the largest!",
           fontface="bold", size=4, color="blue", angle=45)
```

<br>

# Hotel Bookings

## Comparison of market segments by hotel type for hotel bookings

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}

hotel_bookings <- read.csv("C:/Users/tpess/OneDrive/Ambiente de Trabalho/Google Data Analyst Docs/R/Activities/hotel_bookings.csv")

mindate <- min(hotel_bookings$arrival_date_year)
maxdate <- max(hotel_bookings$arrival_date_year)

ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = market_segment)) +
  facet_wrap(~hotel) + 
  theme(axis.text.x = element_text(angle = 45)) +
  labs(title="Comparison of market segments by hotel type for hotel bookings",
       subtitle=paste0("Data from: ", mindate, " to ", maxdate),
       x="Market Segment",
       y="Number of Bookings")
```